Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
\begin{verbatim}
For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

@@

\begin{verbatim}
The current paper includes in sub-section 
`2.1. Selecting an appropriate forecasting method' (former
sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
 and ELM (requested by Reviewer #2).

Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
the results obtained with the two last methods have been included in 
this new version of the paper.
\end{verbatim}
% Antonio - TODO: say where are these results (table/figure/page)

~\\
\noindent (2) \emph{For RF, how many trees are set? }

\begin{verbatim}
As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, 
it has been mentioned that the best performance was obtained with a 
number of trees equal to 50.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

@@

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion. 
% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
The reviewer is right, thus, we have revised the whole paper referring 
to the term `regression' instead of `classification'. Moreover this have 
been also addressed solving the issue related to comment #1, where the
application procedure of feature selection methods for regression problems 
has been clarified. 
\end{verbatim}
% Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
% you are right... but the way the reviewer has expressed it is quite strange.

@@

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts of the 
text and several paragraphs have been rewritten in order to make 
them shorter, clearer and to improve its comprehension.

Also, several tables have been moved to the Appendix and that
data has been presented now as the new Figure 3.

Finally, the paper has been completely revised and several 
typographic errors have been fixed.

We are very grateful for your valuable suggestions and comments. 
\end{verbatim}
% Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.
% we have to say: "Paragraph #X in subsection #Y" (naming the paragraphs that we identified and gathered-joined)

@@

\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\

\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }

\begin{verbatim}
Following the reviewer's request, we have conducted several new experiments 
and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
 Figures AA, BB accordingly. 
A description of both approaches have been also included in subsection 2.1.

In addition new references has been added to the paper related to these 
methods, namely [REF_XX, REF_YY].
\end{verbatim}
% Antonio - TODO: Complete with the number of tables and figures, along with the new references
% I don't know what references have been added in this revision. I'll ask Hossam.

@@

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included this new text:

"Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers."

Also, in the next-to-last paragraph, we have laid out our 
methodology and clarified the main contributions of this paper 
to the state of the art.
\end{verbatim}
% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches. Maybe the use of real data is a good point. And also emphasize the contribution to the SotA.
% well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)

@@

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future work section, at the end 
of Section 7 (see page XX).
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

@@

********* TO WRITE ***********

\end{verbatim}
% Antonio - TODO: we can't write the same answer for two reviewers. We'll answer the same, once we have the response for the previour reviewer but in other words. ;)

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized these sub-sections, 
moving them to section 2.
\end{verbatim}
% Antonio - TODO: we have also to link them properly to the new section and to remove them from the text describing Section 4 where they were... Then, say this in the response.
% I have linked them, but I think we should leave that sentence in Section 4 refering to the methods we have used.

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure XX 
at page YY).
\end{verbatim}
% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
% Almost every paper I have read (and that has been cited in the SotA) shows a very generic flowchat

@@

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
We have improved Section 5, including the parameter settings of 
M5P, kNN and RF methods (see paragraph XX at page YY).

The authors want to express our gratitude to this reviewer 
for his/her suggestions.
\end{verbatim}
% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
% Could we use a table for showing them easily?
% Antonio - TODO: say paragraph/page where they are.

% Antonio - TODO: Say if there are new references and include them in a final section in this letter.
% yes, there are some, but is Hossam who knows what references have been added in this revision.
%------------------------------------------------------------------------------------
\section{New references added in this revision}

[XX] Authors, Title, Journal, pages, Year

[YY] Authors, Title, Journal, pages, Year

[ZZ] Authors, Title, Journal, pages, Year

\end{document}

### 2016-09-07 paper.tex
clarifying some details in section-6

In this stage of the experiments for the special cases, the
feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and
targets, might in fact include different factors or have different
leverage when deciding how much to print. 
For clarity purpose, obtained results have been shown in Tables
\ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
in the appendix of tables at the end of this paper.
In those tables it can be seen that, as in the previous experiment, the highest 
predictive power is exhibited by RFE over CSE and SOM feature selection methods.
In this sense, RFE reduction has noticeably improved the performance of all models, 
specially in the case of the best selling publisher house (i.e. UDL929) and the 
publisher which publishes a wide range of different books (i.e. UDL704).

>>>>

In this stage of the experiments for the special cases, the
feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and
targets, might in fact include different factors or have different
leverage when deciding how much to print. 
For clarity purpose, obtained results after applying feature selection methods
have been shown in Tables \ref{Table:case1results_no_fs} to \ref{Table:case4results_fs_som}
in the appendix of tables at the end of this paper.
In those tables it can be seen that, as in the previous experiment, the highest 
predictive power is exhibited by RFE over CSE and SOM feature selection methods.
In this sense, RFE reduction has noticeably improved the performance of all models, 
specially in the case of the best selling publisher house (i.e. UDL929) and the 
publisher which publishes a wide range of different books (i.e. UDL704).
